Kindly Bent to Free Us

### 2020-06-03 kindly/infer/infer.tex
cosmetics

These properties
are sufficient to state that $HM(\CL)$ provides principal type inference.
The next section states that this properties carries over to our extension
of \hmx
with kind inference, affine types and borrows.
%
This algorithm also simplifies constraints significantly.
All the simplification mechanisms presented
here, including the variance-based one, are complete.
It is also possible to add ``best-effort'' simplification
rules which help reduce the size of inferred signatures even further
\citep{DBLP:conf/aplas/Simonet03}.

@@

The extended inference algorithm still satisfies the soundness
and completeness properties of \hmx.
% This is achieved by extending
% the original proofs from \hmx, which is done in \cref{appendix:infer}.
%
The first theorem states that our inference algorithm is sound
with respect to the syntax-directed type system.

@@

The syntax-directed derivation holds with the usage environment $\Sv$ instead of the originally provided environment $\E$. Indeed,
$\E$ does not contain suspended and borrow bindings, since those
are discovered on the fly and recorded in $\Sv$. The type binding, however,
are directly taken from the syntax-directed derivation.

The second theorem states that our algorithm is complete: for any given
syntax-directed typing derivation, our inference algorithm can find
a derivation that gives a type at least as general.
% For this, we need first to provide a few additional definitions.

>>>>

These properties
are sufficient to state that $HM(\CL)$ provides principal type inference.
The next section shows that these properties carry over to the
inference algorithm for our extension
of \hmx
with kind inference, affine types, and borrows.
%
This algorithm includes sound and complete constraint simplification.
In addition, we may add ``best-effort'' simplification
rules which help reduce the size of inferred signatures 
\citep{DBLP:conf/aplas/Simonet03}.

@@

The extended inference algorithm is sound
and complete with respect to our extension of \hmx.
% This is achieved by extending
% the original proofs from \hmx, which is done in \cref{appendix:infer}.
%
The first theorem states that inference is sound
with respect to the syntax-directed type system.

@@

The syntax-directed derivation holds with the usage environment $\Sv$ instead of the originally provided environment $\E$. Indeed,
$\E$ does not contain suspended and borrow bindings. Those
are discovered on the fly and recorded in $\Sv$. Type bindings
are taken directly from the syntax-directed derivation.

The second theorem states that inference is complete: for any given
syntax-directed typing derivation, our inference algorithm can find
a derivation that gives a type at least as general.
% For this, we need first to provide a few additional definitions.
